\SW: I. Crowd-sourcing the Discovery of Gravitational Lenses

### 2013-06-13 doc/sw-system.tex

Indeed, the information content of each classification can be estimated by an
agent before the next classification is made, just from its confusion matrix.
We define the expected contributed information per classification, as
\be
  \langle I_k \rangle = \frac{1}{2} 
                        \sum_{i} \left( \mathcal{M}^k_{i}  
              + \mathcal{M}^k_{i}\cdot\log_2{\mathcal{M}^k_i} \right),
  \label{eq:app:info}
\ee
where $i$ runs over all 4 elements of the confusion matrix 
$\mathcal{M}^k_i$, and $\langle I_k \rangle$ is measured in ``bits.'' 
The second term in the sum is recognisable as a
negative entropy, while the first term and the factor of 1/2
account for the way the confusion matrix encodes the results for the
classification of two types of subject, and that the probabilities
associated with each type are normalised. \Eref{eq:app:info} gives the
required result, that 
both the hypothetical {\it perfect} and
{\it obtuse} classifiers contribute 
1 bit of information each, per classification.

In fact, the only classifier that contributes the minimum information per
classification, zero bits, is the {\it random} classifier, whose agent's
confusion matrix elements are all 0.5.   
We conservatively initialise all the agents' confusion matrices to be that of
the random classifier. This makes no allowance for volunteers that actually do
have previous experience of what gravitational lenses look like, but should
help prevent large numbers of false positives being assigned high probability.
Plotting  $\langle I_k \rangle$ as a function of time will, to some extent,
illustrate the
learning process undergone by the $k^{\rm th}$ volunteer-agent partnership.

@@

>>>>

Indeed, the information content of each classification can be estimated by an
agent before the next classification is made, just from its confusion matrix.
The Shannon entropy generated by a classifier upon performing a
classification is
\be
  \langle S_k \rangle =  
   -P_{\rm right}\cdot\log_2{P_{\rm right}} -  P_{\rm wrong}\cdot\log_2P_{\rm wrong}\,,
\ee
where $P_{\rm right}$ and $P_{\rm wrong}$ are the averages of the diagonal and
the off-diagonal elements of the confusion matrix, respectively, and $\langle
S_k \rangle$ is measured in ``bits.'' These averages represent the probability
of a classifier to get a classification right or wrong, respectively. We define
the information contributed by a classifier as
\begin{equation}
I_k = 1 - S_k\,.
  \label{eq:app:info}
\end{equation}
\Eref{eq:app:info} gives the required result, that both the hypothetical {\it
perfect} and {\it obtuse} classifiers contribute 1 bit of information each, per
classification. Classifiers whose agent's confusion matrix is such that $P_{\rm
right}=P_{\rm wrong}=0.5$, contribute zero bits of information. Such users
identify a lens correctly with the same probability as they misclassify a dud
image to contain a lens, and thus their classification is of no value.

We conservatively initialise all the elements of the agents' confusion matrices
to be 0.5, that of a random classifier. This makes no allowance for volunteers
that actually do have previous experience of what gravitational lenses look
like, but should help prevent large numbers of false positives being assigned
high probability. Plotting  $\langle I_k \rangle$ as a function of time will,
to some extent, illustrate the learning process undergone by the $k^{\rm th}$
volunteer-agent partnership.

@@

The confusion matrix obtained from the application of Equation
(\ref{eq:app:fraction}) has some inherent noise which reduces as the number
of training subjects classified by the user increases. For simplicity, the
discussion thus far assumed the case when the confusion matrix is known
perfectly. Let us first discuss how to characterize the noise in the confusion
matrix. ** This needs work **

For ease of notation, we will denote $\pr(C_k|\LENS,T_k)\equiv p_L$ and
$\pr(C_k|\NOT,T_k)\equiv p_N$. In reality, there is a probability distribution
for both $p_L$ and $p_N$. Let $p_0$ be the prior probability of the subject
being a lens. Then the posterior probability, $p_0'$ of the subject being a
lens after the classification $C_k$ is
\be
  \label{eq:app:sec}
p_0' = \frac{p_L p_0}{\left[ p_L p_0 + p_N (1- p_0) \right]},
\ee
The posterior probability distribution $p_0'$ can be obtained by marginalizing
over the probability distributions of $p_L$, $p_N$ and the prior probability
distribution $p_0$ such that,
\be
P(p_0') = \int p_0' P(p_L) P(p_N) P(p_0) dp_L dp_N dp_0\,.
\ee
This marginalization is not analytically tractable. Therefore, we have
implemented the following Monte-Carlo solution for this problem.

%Finally, we also need to update the confusion matrix of an agent and obtain the
%variance on each element of the matrix, once a training subject has been
%classified. We would like to derive the posterior probability of the
%probability elements $p_1$ and $p_2$ given their prior probabilities. For this
%purpose, we can again make use of Bayes' theorem,
%\begin{equation}
%P(p_x'|N_{"X"},N_X,T) = \frac{P(N_{``X"}|p_x',N_X,T) P(p_x'|N_X,T)}{\sum_{N_{``X"}} P(N_{``X"}|p_x',N_X,T) P(p_x'|N_X,T)}
%\end{equation}
%Here, $P(N_{``X"}|p_x',N_X,T)$ is a binomial distribution, although this is not
%true strictly speaking given that our agents are learning and the values of the
%confusion matrix are moving. Modelling the learning curve of our users is yet
%another complicated extension we could think about.
